### 2024-09-06 cognitive-bias.qmd
20240906 - expand example

The *availability heuristic* refers to the tendency for a person's judgments or predictions about the frequency or probability of something to be made based on how readily instances can be brought to mind.
For instance, when making fantasy predictions about a player, more recent big performance games may more easily come to mind compared to lower-scoring games and games that occurred longer ago.
Thus, a manager may be more inclined to pick players to start who had more recent, stronger performances rather than players who have higher long-term averages.

>>>>

The *availability heuristic* refers to the tendency for a person to make judgments or predictions about the frequency or probability of something based on how readily instances can be brought to mind.
For instance, when making fantasy predictions about a player, more recent big performance games (or games that receive more news coverage) may more easily come to mind compared to lower-scoring games and games that occurred longer ago.
Thus, a manager may be more inclined to pick players to start who had more recent, stronger performances rather than players who have higher long-term averages.
